Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Did thing.

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb, amsrefs}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{breqn}
\usepackage[]{algorithm2e}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{object-render3.png}
    \caption{A sample render of ten spheres and their shadows.  The light source used was made up of nine point light sources, grouped together very closely.}
    \label{fig:render_3}
\end{figure}

To further explain the algorithm behind this method, first let us describe how the object would be represented.  The method used is most similar to the second representation of objects discussed previously, as spheres and cylinders in a graph layout.  Each object would consist of a list of nodes or spheres $W$, a list of edges or cylinders $E$, and a radius $r$.  The nodes in $W$ are described using 3-tuples of floating point numbers, representing their location in Cartesian 3-space, and the edges in $E$ are represented by 2-tuples of indexes, referencing the two nodes in $W$.  The algorithm iterates over the nodes in $W$, creating spheres of radius $r$.  Then, it iterates over the edges in $E$, creating cylinders with radius $r$ and endpoints centered on the

@@

\begin{dmath*}
\vec{l} = position of light\\
\vec{r} = the radius of each sphere and cylinder\\
spheres = a list of positions of centers of spheres\\
cylinders = a list of pairs of positions specifying the end faces of the cylinders
\end{dmath*}

\begin{algorithm}[H]
\DontPrintSemicolon
 \KwData{$\vec{l}$ = position of light, $\vec{r}$ = the radius of each sphere and cylinder, $spheres$ = a list of positions of centers of spheres, $cylinders$ = a list of pairs of positions specifying the end faces of the cylinders}
 \KwResult{$pixels$ = array of black and white pixels indicating on which areas of the wall light is incident}
 $pixels \leftarrow$ a uniformly white (illuminated) image of the desired size\;
 \For{each sphere in spheres}{
  read current\;
  \eIf{understand}{
   go to next section\;
   current section becomes this one\;
   }{
   go back to the beginning of current section\;
  }
 }
 \For{each cylinder in cylinders}{
  \tcp*[h]{similar to the above but cylinders cast different}
  \tcp*[h]{shaped shadows}\\
  \tcp*[h]{This case is not handled by our code.}
 }
 \caption{first shadow rendering method}
\end{algorithm}

for each sphere in spheres:
	if the sphere is entirely above the light or below the shadow plane:
		it casts no shadow; continue to the next sphere
	if the top of the sphere is beneath the light and the bottom is above the plane:
		The shadow cast on the plane will be elliptical.
		Calculate the equation of the cone formed by all lines passing through the
				light source and tangent to the sphere.
		Find the equation of the ellipse by intersecting this cone with the shadow
				plane.
		The equation has the form $A*x^2 + B*y^2 + C*x*y + D*x + E*y + F = 0$.
		Rearrange the equation to have the form $G(x)*y^2 + H(x)*y + I(x) = 0$, where
				$G$, $H$, and $I$ are 2nd order or lower polynomials in $x$.
		For each column $c$ in pixels:
			Find the value of $x$ that corresponds to $c$.
			Calculate $G(x)$, $H(x)$, and $I(x)$.
			Use the quadratic formula to find two values of $y$ satisfying the
					equation for the boundary of the ellipse.
			Convert the values of y to row coordinates in the image.
			In column $c$ and all rows $r$ between the two calculated:
				color pixels[r][c] black
	if the sphere intersects the shadow plane:
		Handling this case is at least as complicated as handling a sphere strictly
				above the plane.
		The circular intersection of the circle and the plane is shadowed.
		Any additional shadowing is a subset of the elliptical shadow described in
				the previous case.
		This case is not handled by our code.
	if the sphere intersects the light:
		Color all of pixels black.
		Return from the proceedure early.
		This case is not handled by our code.
	if the top of the sphere is above the light, its bottom below the light, without
			intersecting it:
		The shadow cast is hyperbolic.
		This case is not handled by our code, but it would likely be similar to
				the case of elliptical shadows.

@@

The simplest method of representing nodes and edges would be to keep the number of both constant, moving the nodes around while retaining the same edge mappings for all genomes.  This way, one could represent each node as an unsigned integer, or an array of three unsigned integers representing the positive incremental distance from some origin point.  Given the nature of the problem, one can disregard any space not within the projection from the light source to a given section of the wall.  This allows the bounding of the entire system in a cube, which we can use to define our \texttt{0} and our \texttt{MAX\_INT} for each coordinate direction.  Next, we would create an array of unsigned integers, of length 3 times the number of nodes in the system.  This would be the genome for the genetic algorithm.  The fitness function would be defined as the number of matching pixels (within a certain threshold) between the input and the generated shadow using one of the shadowmapping methods above.  Using such a method would prevent situations where the graph became unconnected, but it does not address issues of structural integrity any further than this.  Since the nature of the problem allows for many local solutions, the ability of such a genetic algorithm to converge may be slowed.

One may increase the variability of the genetic algorithm by introducing edge mapping to the genome.  One may represent an edge between node A and node B as a 1 in a symmetric n-by-n adjacency matrix, where n is the number of nodes in the graph.  This allows for easy genetic recombinations, with the ability to vary the number of edges in the graph.  The issue that this does not take care of is the connectivity of the graph.  One would have to either add a penalty to the fitness function which performed a depth-first search on the nodes and penalized unconnected graphs, or alternatively, one could modify the base constructs of the genetic algorithm, making it continue to perform attempts at combining two genomes until it had children that were all fully connected.  For the first option, the question would become how strongly one would decrease the fitness of an unconnected graph, and whether the number of unconnected pieces should increase that penalty.  The second option would allow us to use the same fitness function, but may add extra levels of complexity to the problem due to the required repeated attemps within single generations.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_1.png}
    \caption{Depicted is the light source, a sphere, and a ray of light tangent to the sphere (labeled as generatrix of cone).}
    \label{fig:shadow_1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_2.png}
    \caption{This figure includes in addition the orthogonal projection from the point of tangency to the axis of the cone. The distance $L''$ is from the light source to the tip of the projection vector.}
    \label{fig:shadow_2}
\end{figure}

@@

\begin{bibdiv}
 \begin{biblist}
  \bib{Dasgupta}{book}{
   title={Algorithms},
   author={Dasgupta, Sanjoy},
   author={Papadimitriou, Christos},
   author={Vazirani, Umesh},
   publisher={McGraw-Hill Education},
   address={New York},
   year={2006}  
  }
 \end{biblist}
\end{bibdiv}

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{breqn}
\usepackage{alltt}

@@

@@

\begin{alltt}
for each sphere in spheres:
  if the sphere is entirely above the light or below the shadow plane:
    it casts no shadow; continue to the next sphere
  if the top of the sphere is beneath the light and the bottom is above the plane:
    The shadow cast on the plane will be elliptical.
    Calculate the equation of the cone formed by all lines passing through the
        light source and tangent to the sphere.
    Find the equation of the ellipse by intersecting this cone with the shadow
        plane.
    The equation has the form A*x^2 + B*y^2 + C*x*y + D*x + E*y + F = 0$.
    Rearrange the equation to have the form $G(x)*y^2 + H(x)*y + I(x) = 0$, where
        \(G\), \(H$, and \(I\) are 2nd order or lower polynomials in \(x\).
    For each column \(c\) in pixels:
      Find the value of \(x\) that corresponds to \(c\).
      Calculate \(G(x)\), \(H(x)\), and \(I(x)\).
      Use the quadratic formula to find two values of \(y\) satisfying the
          equation for the boundary of the ellipse.
      Convert the values of y to row coordinates in the image.
      In column \(c\) and all rows \(r\) between the two calculated:
        color pixels[r][c] black
  if the sphere intersects the shadow plane:
    Handling this case is at least as complicated as handling a sphere strictly
        above the plane.
    The circular intersection of the circle and the plane is shadowed.
    Any additional shadowing is a subset of the elliptical shadow described in
        the previous case.
    This case is not handled by our code.
  if the sphere intersects the light:
    Color all of pixels black.
    Return from the proceedure early.
    This case is not handled by our code.
  if the top of the sphere is above the light, its bottom below the light, without
      intersecting it:
    The shadow cast is hyperbolic.
    This case is not handled by our code, but it would likely be similar to
        the case of elliptical shadows.

\end{alltt}

@@

The simplest method of representing nodes and edges would be to keep the number of both constant, moving the nodes around while retaining the same edge mappings for all genomes.  This way, one could represent each node as an unsigned integer, or an array of three unsigned integers representing the positive incremental distance from some origin point.  Given the nature of the problem, one can disregard any space not within the projection from the light source to a given section of the wall.  This allows the bounding of the entire system in a cube, which we can use to define our \texttt{0} and our \texttt{MAX\_INT} for each coordinate direction.  Next, we would create an array of unsigned integers, of length 3 times the number of nodes in the system.  This would be the genome for the genetic algorithm.  The fitness function would be defined as the number of matching pixels (within a certain threshold) between the input and the generated shadow using one of the methods above.  Using such a method would prevent situations where the graph became unconnected, but it does not address issues of structural integrity any further than this.  Since the nature of the problem allows for many local solutions, the ability of such a genetic algorithm to converge may be slowed.

One may increase the variability of the genetic algorithm by introducing edge mapping to the genome.  One may represent an edge between node A and node B as a 1 in a symmetric n-by-n adjacency matrix, where n is the number of nodes in the graph.  This allows for easy genetic combinations, with the ability to vary the number of edges in the graph.  The issue that this does not take care of is the connectivity of the graph.  One would have to either add a penalty to the fitness function which performed a depth-first search on the nodes and penalized unconnected graphs, or alternatively, one could modify the base constructs of the genetic algorithm, making it continue to perform attempts at combining two genomes until it had children that were all fully connected.  For the first option, the question would become how strongly one would decrease the fitness of an unconnected graph, and whether the number of unconnected pieces should increase that penalty.  The second option would allow us to use the same fitness function, but may add extra levels of complexity to the problem due to the required repeated attemps within single generations.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_1.png}
    \caption{Depicted is the light source, a sphere, and a ray of light tangent to the sphere (labeled as generatrix of cone).}
    \label{fig:shadow_1}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_2.png}
    \caption{This figure includes in addition the orthogonal projection from the point of tangency to the axis of the cone. The distance $L''$ is from the light source to the tip of the projection vector.}
    \label{fig:shadow_2}
\end{figure}

@@
